Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-21 paper.tex
mimic CEK syntax in PL&LambdaCalculi
bisim relation for SC and D

\newcommand{\kOOmt}[0]{\square}
\newcommand{\kOOconsI}[3]{#3[\mathtt{cons} \; \square \; \langle#1,#2\rangle ]}
\newcommand{\kOOconsII}[2]{#2[\mathtt{cons} \; #1 \; \square]}
\newcommand{\kOOinl}[1]{#1[\mathtt{inl} \; \square]}
\newcommand{\kOOinr}[1]{#1[\mathtt{inr} \; \square]}
\newcommand{\kOOappI}[3]{
	#3[\square \; \langle#1,#2\rangle ]
}
\newcommand{\kOOappII}[2]{
	#2[#1 \; \square]}
\newcommand{\kOOcar}[1]{#1[\mathtt{fst} \; \square]}
\newcommand{\kOOcdr}[1]{#1[\mathtt{snd} \; \square]}
\newcommand{\kOOcaseI}[4]{
	#4[\mathtt{case} \; \square \; \langle#1,#3\rangle \; \langle#2,#3\rangle ]}
\newcommand{\kOOcaseII}[4]{
	#4[\mathtt{case} \; #1 \; \square \; \langle#2,#3\rangle ]}
\newcommand{\kOOcaseIII}[3]{
	#3[\mathtt{case} \; #1 \; #2 \; \square]}
\newcommand{\kOOcast}[2]{
	#2[\square \langle #1 \rangle]}

@@

\newcommand{\typingHC}[3]{#1 : #2 \Longrightarrow #3}
\newcommand{\hcvOOinj}[2]{\mathtt{inj} \; #2}
%\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
\newcommand{\hcvOOfun}[5]{\mathtt{fun}^{\POOfun{#1}{#5}} \; #2 \; #3 \; #4}
\newcommand{\hcvOOtt}[0]{\mathtt{unit}}
%\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\;#2\;#3\;#4}
\newcommand{\hcvOOcons}[4]{\mathtt{cons}^{\POOprod{#2}{#4}}\;#1\;#3}
%\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\;#2}
%\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\;#2}
\newcommand{\hcvOOinl}[2]{\mathtt{inl}^{#2}\;#1}
\newcommand{\hcvOOinr}[2]{\mathtt{inr}^{#2}\;#1}
\newcommand{\hckOOmt}[0]{\mathtt{stop}}
\newcommand{\hckOOconsI}[3]{\mathtt{cons_1}\;#1\;#2\;#3}
\newcommand{\hckOOappII}[2]{\mathtt{app_2}\;#1\;#2}
\newcommand{\sidecond}[1]{\text{if}\;#1}
% Lazy D cast calculus on space-inefficient CEK
\newcommand{\judgeCreduce}[2]{#1 \longmapsto_{\mathcal{C}} #2}
\newcommand{\judgeCreduceTrans}[2]{#1 \longmapsto_{\mathcal{C}}^{*} #2}
\newcommand{\judgeCeval}[2]{eval_{\mathcal{C}}(#1) = #2}
\newcommand{\redrule}[3]{#1 & \longmapsto_\mathcal{C} & #2 & #3\\}
\newcommand{\hiredrule}[3]{\highlight{#1} & \highlight{\longmapsto_\mathcal{C}} & \highlight{#2} & \highlight{#3} \\}
% blame calculus on space-efficient CEK
\newcommand{\judgeSreduce}[3]{#2 \longmapsto_{\mathcal{S}(#1)} #3}
\newcommand{\judgeSreduceTrans}[3]{#2 \longmapsto_{\mathcal{S}(#1)}^{*} #3}
\newcommand{\judgeSeval}[3]{eval_{\mathcal{S}(#1)}(#2) = #3}
\newcommand{\redruleS}[3]{#1 & \longmapsto_{\mathcal{S}(C)} & #2 & #3\\}
\newcommand{\hiredruleS}[3]{\highlight{#1} & 
\highlight{\longmapsto_{\mathcal{S}(C)}} & \highlight{#2} & \highlight{#3} \\}
% Normal Coercion
\newcommand{\ncProj}[2]{#1?^{#2}}
\newcommand{\ncInj}[1]{#1!}
\newcommand{\ncId}[0]{\iota}
\newcommand{\ncSeq}[2]{#1;#2}
\newcommand{\ncFail}[1]{\bot^{#1}}
\newcommand{\ncFun}[2]{\POOfun{#1}{#2}}
\newcommand{\ncProd}[2]{\POOprod{#1}{#2}}
\newcommand{\ncSum}[2]{\POOsum{#1}{#2}}
% Hypercoercion
\newcommand{\hyperCoercionI}[0]{\mathtt{id\star}}
\newcommand{\hyperCoercionC}[3]{#1 \overset{#2}{\curvearrowright} #3}
% machine state simulations
\newcommand{\eqvS}[4]{#3 \approx_{\mathcal{S}\mathcal{S}} #4}
\newcommand{\eqvSD}[3]{#2 \approx_{\mathcal{SD}} #3}
% to-dos
\newcommand{\todoKC}[1]{\todo[inline]{KC needs to #1}}
\newcommand{\todoKCFixed}[0]{\todo[inline]{Fixed. -KC}}
% abbrev
\newcommand{\castCalculus}[0]{$\lambda_{\rightarrow}^{\langle\cdot\rangle}$}
% names
\newcommand{\ineffCEK}{$\mathcal{C}$}
\newcommand{\ineffCEKD}{$\mathcal{D}$}
\newcommand{\ineffCEKUD}{$\mathcal{UD}$}
\newcommand{\judgeDreduce}[2]{#1 \longmapsto_{\mathcal{D}} #2}
\newcommand{\judgeDreduceTrans}[2]{#1 \longmapsto_{\mathcal{D}}^{*} #2}
\newcommand{\judgeDeval}[2]{eval_{\mathcal{D}}(#1) = #2}
\newcommand{\judgeUDreduce}[2]{#1 \longmapsto_{\mathcal{UD}} #2}
\newcommand{\judgeUDreduceTrans}[2]{#1 \longmapsto_{\mathcal{UD}}^{*} #2}
\newcommand{\judgeUDeval}[2]{eval_{\mathcal{UD}}(#1) = #2}
\newcommand{\effCEK}[1]{$\mathcal{S}(#1)$}
\newcommand{\evalEqv}[2]{$eval_{\text{#1}} = eval_{\text{#2}}$}
\newcommand{\continue}[2]{continue(#2,#1)}
\newcommand{\highlight}[1]{{\color{red} #1}}

@@

	\stxrule{v}{values}{
		\hcvOOtt \mid
		\hcvOOfun{c}{\rho}{x}{e}{c} \mid
		\hcvOOcons{v}{c}{v}{c}
	}
	\stxrulecont{
		\hcvOOinl{v}{c} \mid
		\hcvOOinr{v}{c} \mid
		\hcvOOinj{P}{v}
	}
%	\stxrule{r}{cast results}{
%		\rOOsucc{v} \mid
%		\rOOfail{l}
%	}
%	\stxrule{s}{states}{
%		\sOOinspect{e}{\rho}{\kappa} \mid{}
%		\sOOreturn{v}{\kappa} \mid{}
%		\sOOhalt{o}
%	}
	\stxrule{\kappa}{continuation}{
		\langle c \rangle k
	}
	\stxrule{k}{pre-continuations}{
		\hckOOmt \mid{}
		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{cons_2} \; v \; \kappa \mid{}
		\mathtt{inl} \; \kappa \mid{}
		\mathtt{inr} \; \kappa
	}
	\stxrulecont{
		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{app_2} \; v \; \kappa \mid{}
		\mathtt{fst} \; \kappa \mid{}
		\mathtt{snd} \; \kappa
	}
	\stxrulecont{
		\mathtt{case_1} \; e \; e \; \rho \; \kappa \mid
		\mathtt{case_2} \; v \; e \; \rho \; \kappa \mid{}
		\mathtt{case_3} \; v \; v \; \rho \; \kappa
	}
	\end{array}
	\]

	Build continuation \fbox{$cont(k) = \kappa$}
	\[
	\begin{array}{rclc}
	\funrule{cont(k)}{\langle id(T_1) \rangle k}{
		\sidecond{k : T_1 \Longrightarrow T_2}}
	\end{array}
	\]

	Extend continuation \fbox{$ext(c,\kappa) = \kappa$}
	\[
	\begin{array}{rclc}
	\funrule{ext(c_1,\langle c_2 \rangle k)}{\langle seq(c_1,c_2) \rangle k}{}
	\end{array}
	\]

@@

	\redruleS{
		\sOOinspect{(\eOOcase{e_1}{e_2}{e_3})}{\rho}{\kappa}}{
		\sOOinspect{e_1}{\rho}{cont(\kOOcaseI{E}{e_2}{e_3}{\kappa})}}{}
	\hiredruleS{
		\sOOreturn{v}{\langle c \rangle k}
	}{
	\begin{cases}
	continue(k,v') & \sidecond{applyCast(v,c) = \rOOsucc{v'}} 
	\\
	\sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(v,c) = \rOOfail{l}}
	\end{cases}
	}{}
%\redruleS{
%	\sOOreturn{v_1}{(\kOOconsI{e_2}{\rho}{\kappa})}}{
%	\sOOinspect{e_2}{\rho}{cont(\kOOconsII{v_1}{\kappa})}}{}
%
%\redrule{
%\sOOreturn{v_2}{(\kOOconsII{v_1}{\kappa})}}{
%\sOOreturn{(\hcvOOcons{v_1}{id(T_1)}{v_2}{id(T_2)})}{\kappa}}{
%\\&&
%\sidecond{v_1 : T_1 \wedge v_2 : T_2}}
%
%\redrule{
%\sOOreturn{v}{(\kOOinl{\kappa})}}{
%\sOOreturn{(\hcvOOinl{v}{id(T)})}{\kappa}}{
%\\&&
%\sidecond{v : T}}
%
%\redrule{
%\sOOreturn{v}{(\kOOinr{\kappa})}}{
%\sOOreturn{(\hcvOOinr{v}{id(T)})}{\kappa}}{
%\\&&
%\sidecond{v : T}}
%
%\redrule{
%\sOOreturn{v_1}{(\kOOappI{e_2}{\rho}{\kappa})}}{
%\sOOinspect{e_2}{\rho}{cont(\kOOappII{v_1}{\kappa})}}{}
%
%	
%	& \vdots \\
%	\redruleS{
%		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
%	}{
%		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
%	}{}
%	\redruleS{
%		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
%	}{
%		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
%	}{}
%	\redruleS{
%		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
%	}{
%		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
%	}{}
%	\redruleS{
%		
%\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
%	}{
%		\begin{cases}
%		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)} \\
%		\;\;\;\;\;\;\;\;\;\sidecond{applyCast(v,c_1) = \rOOsucc{v'}} 
%		\\
%		\sOOhalt{(\oOOblame{l})} \\
%		\;\;\;\;\;\;\;\;\;\sidecond{applyCast(v,c_1) = \rOOfail{l}}
%		\end{cases}
%		
%	}{}
	\end{array}
	\]

@@

\subsection{\lazyD\ Cast ADTs Respect \ineffCEKD\ if They are 
Monoids}
\label{secc:framework:monoid-correct}

In this subsection, we prove that if a instance of Cast ADT $C$ is Lazy D and 
is a monoid, then $eval_\mathcal{D} = eval_{\mathcal{S}(C)}$. We proof this 
theorem with a weak bisimulation between \ineffCEKD\ and 
\effCEK{C}.

@@

The relation between values is more special. When the \ineffCEKD\ value is 
non-casted, the casts in the \effCEK{C} value are identity. Otherwise, we push 
the cast into the value constructors, except injections. For examples: 
\begin{gather*}
\inference{
	v_1, v_2 : P &
	v_1 \approx v_2
}{
	\hcvOOinj{P_1}{v_1} \approx \vOOcast{v_2}{\cOOcast{P}{l}{\TOOdyn}}
}
\quad
\inference{
	v_1, v_2 : T &
	v_1 \approx v_2
}{
	\hcvOOinl{v_1}{id(T)} \approx \vOOinl{v_2}
}
\quad
\inference{
	(\hcvOOinl{v}{c}, v_2) : \POOsum{T_1}{T_2}
}{
	\hcvOOinl{v}{seq(c,cast(T_1,l,T_3))} \approx 
	\vOOcast{v_2}{\cOOcast{T_1}{l}{T_3}}
}
%\quad
%\inference{
%	\Gamma , x : T_1 \vdash T_2 &
%	\rho_1 \approx \rho_2
%}{
%	\hcvOOfun{id(T_1)}{\rho_1}{x}{e}{id(T_2)} \approx \vOOfun{\rho_2}{x}{e}
%}
%\quad
%\inference{
%	\hcvOOcons{v_1}{c_1}{v_2}{c_2}
%	\approx
%	v
%}{
%	\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))}
%}
%\\
%\inference{
%	\hcvOOfun{c_1}{\rho}{x}{e}{c_2} : \POOfun{T_1}{T_2} &
%	\hcvOOfun{c_1}{\rho}{x}{e}{c_2} \approx v
%}{
%	\hcvOOfun{seq(cast(T_3,l,T_1), c_1)}{\rho}{x}{e}{seq(c_2,cast(T_2,l,T_4))}
%	\approx
%	\vOOcast{v}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T3}{T_4}}}
%}
\end{gather*}

>>>>

\newcommand{\kOOmt}[0]{\mathtt{stop}}
\newcommand{\kOOconsI}[3]{[\mathtt{cons} \; \square \; \langle#1,#2\rangle ]#3}
\newcommand{\kOOconsII}[2]{[\mathtt{cons} \; #1 \; \square]#2}
\newcommand{\kOOinl}[1]{[\mathtt{inl} \; \square]#1}
\newcommand{\kOOinr}[1]{[\mathtt{inr} \; \square]#1}
\newcommand{\kOOappI}[3]{
	[\square \; \langle#1,#2\rangle ]#3
}
\newcommand{\kOOappII}[2]{
	[#1 \; \square]#2}
\newcommand{\kOOcar}[1]{[\mathtt{fst} \; \square]#1}
\newcommand{\kOOcdr}[1]{[\mathtt{snd} \; \square]#1}
\newcommand{\kOOcaseI}[4]{
	[\mathtt{case} \; \square \; \langle#1,#3\rangle \; \langle#2,#3\rangle ]#4}
\newcommand{\kOOcaseII}[4]{
	[\mathtt{case} \; #1 \; \square \; \langle#2,#3\rangle ]#4}
\newcommand{\kOOcaseIII}[3]{
	[\mathtt{case} \; #1 \; #2 \; \square]#3}
\newcommand{\kOOcast}[2]{
	[\square \langle #1 \rangle]#2}

@@

\newcommand{\typingHC}[3]{#1 : #2 \Longrightarrow #3}
\newcommand{\hcvOOinj}[2]{\mathtt{inj} \; #2}
%\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #2 \; #1 \; #3 \; #4 \; #5}
\newcommand{\hcvOOtt}[0]{\mathtt{unit}}
%\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\;#2\;#3\;#4}
\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\langle#2\rangle\;#3\langle#4\rangle}
%\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\;#2}
%\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\;#2}
\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\langle#2\rangle}
\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\langle#2\rangle}
\newcommand{\hckOOmt}[0]{\mathtt{stop}}
\newcommand{\hckOOconsI}[3]{\mathtt{cons_1}\;#1\;#2\;#3}
\newcommand{\hckOOappII}[2]{\mathtt{app_2}\;#1\;#2}
\newcommand{\sidecond}[1]{\text{if}\;#1}
% Lazy D cast calculus on space-inefficient CEK
\newcommand{\judgeCreduce}[2]{#1 \longmapsto_{\mathcal{C}} #2}
\newcommand{\judgeCreduceTrans}[2]{#1 \longmapsto_{\mathcal{C}}^{*} #2}
\newcommand{\judgeCeval}[2]{eval_{\mathcal{C}}(#1) = #2}
\newcommand{\redrule}[3]{#1 & \longmapsto_\mathcal{C} & #2 & #3\\}
\newcommand{\hiredrule}[3]{\highlight{#1} & \highlight{\longmapsto_\mathcal{C}} & \highlight{#2} & \highlight{#3} \\}
% blame calculus on space-efficient CEK
\newcommand{\judgeSreduce}[3]{#2 \longmapsto_{\mathcal{S}(#1)} #3}
\newcommand{\judgeSreduceTrans}[3]{#2 \longmapsto_{\mathcal{S}(#1)}^{*} #3}
\newcommand{\judgeSeval}[3]{eval_{\mathcal{S}(#1)}(#2) = #3}
\newcommand{\redruleS}[3]{#1 & \longmapsto_{\mathcal{S}(C)} & #2 & #3\\}
\newcommand{\hiredruleS}[3]{\highlight{#1} & 
\highlight{\longmapsto_{\mathcal{S}(C)}} & \highlight{#2} & \highlight{#3} \\}
% Normal Coercion
\newcommand{\ncProj}[2]{#1?^{#2}}
\newcommand{\ncInj}[1]{#1!}
\newcommand{\ncId}[0]{\iota}
\newcommand{\ncSeq}[2]{#1;#2}
\newcommand{\ncFail}[1]{\bot^{#1}}
\newcommand{\ncFun}[2]{\POOfun{#1}{#2}}
\newcommand{\ncProd}[2]{\POOprod{#1}{#2}}
\newcommand{\ncSum}[2]{\POOsum{#1}{#2}}
% Hypercoercion
\newcommand{\hyperCoercionI}[0]{\mathtt{id\star}}
\newcommand{\hyperCoercionC}[3]{#1 \overset{#2}{\curvearrowright} #3}
% machine state simulations
\newcommand{\eqvS}[4]{#3 \approx_{\mathcal{S}\mathcal{S}} #4}
\newcommand{\eqvSD}[3]{#2 \approx_{\mathcal{SD}} #3}
% to-dos
\newcommand{\todoKC}[1]{\todo[inline]{KC needs to #1}}
\newcommand{\todoKCFixed}[0]{\todo[inline]{Fixed. -KC}}
% abbrev
\newcommand{\castCalculus}[0]{$\lambda_{\rightarrow}^{\langle\cdot\rangle}$}
% names
\newcommand{\ineffCEK}{$\mathcal{C}$}
\newcommand{\ineffCEKD}{$\mathcal{D}$}
\newcommand{\ineffCEKUD}{$\mathcal{UD}$}
\newcommand{\judgeDreduce}[2]{#1 \longmapsto_{\mathcal{D}} #2}
\newcommand{\judgeDreduceTrans}[2]{#1 \longmapsto_{\mathcal{D}}^{*} #2}
\newcommand{\judgeDeval}[2]{eval_{\mathcal{D}}(#1) = #2}
\newcommand{\judgeUDreduce}[2]{#1 \longmapsto_{\mathcal{UD}} #2}
\newcommand{\judgeUDreduceTrans}[2]{#1 \longmapsto_{\mathcal{UD}}^{*} #2}
\newcommand{\judgeUDeval}[2]{eval_{\mathcal{UD}}(#1) = #2}
\newcommand{\effCEK}[1]{$\mathcal{S}(#1)$}
\newcommand{\evalEqv}[2]{$eval_{\text{#1}} = eval_{\text{#2}}$}
\newcommand{\continue}[2]{continue(#2,#1)}
\newcommand{\highlight}[1]{{\color{red} #1}}

@@

	\stxrule{v}{values}{
		\hcvOOtt \mid
		\hcvOOfun{c}{\rho}{x}{e}{c} \mid
		\hcvOOcons{v}{c}{v}{c}
	}
	\stxrulecont{
		\hcvOOinl{v}{c} \mid
		\hcvOOinr{v}{c} \mid
		\hcvOOinj{P}{v}
	}
%	\stxrule{r}{cast results}{
%		\rOOsucc{v} \mid
%		\rOOfail{l}
%	}
%	\stxrule{s}{states}{
%		\sOOinspect{e}{\rho}{\kappa} \mid{}
%		\sOOreturn{v}{\kappa} \mid{}
%		\sOOhalt{o}
%	}
	\stxrule{\kappa}{continuation}{
		\kOOcast{c}{k}
	}
	\stxrule{k}{pre-continuations}{
		\kOOmt \mid{}
		\kOOconsI{e}{\rho}{\kappa} \mid
		\kOOconsII{v}{\kappa} \mid
		\kOOinl{\kappa} \mid
		\kOOinr{\kappa}
	}
	\stxrulecont{
		\kOOappI{e}{\rho}{\kappa} \mid
		\kOOappII{v}{\kappa} \mid
		\kOOcar{\kappa} \mid
		\kOOcdr{\kappa}
	}
	\stxrulecont{
		\kOOcaseI{e}{e}{\rho}{\kappa} \mid
		\kOOcaseII{v}{e}{\rho}{\kappa} \mid
		\kOOcaseIII{v}{v}{\kappa}
	}
	\end{array}
	\]

	Build continuation \fbox{$cont(k) = \kappa$}
	\[
	\begin{array}{rclc}
	\funrule{cont(k)}{\kOOcast{id(T_1)}{k}}{
		\sidecond{k : T_1 \Longrightarrow T_2}}
	\end{array}
	\]

	Extend continuation \fbox{$ext(c,\kappa) = \kappa$}
	\[
	\begin{array}{rclc}
	\funrule{ext(c_1,\kOOcast{c_2}{k})}{
		\kOOcast{seq(c_1,c_2)}{k}
	}{}
	\end{array}
	\]

@@

	\redruleS{
		\sOOinspect{(\eOOcase{e_1}{e_2}{e_3})}{\rho}{\kappa}}{
		\sOOinspect{e_1}{\rho}{cont(\kOOcaseI{\rho}{e_2}{e_3}{\kappa})}}{}
	\hiredruleS{
		\sOOreturn{v}{\kOOcast{c}{k}}
	}{
	\begin{cases}
	continue(k,v') & \sidecond{applyCast(v,c) = \rOOsucc{v'}} 
	\\
	\sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(v,c) = \rOOfail{l}}
	\end{cases}
	}{}
%\redruleS{
%	\sOOreturn{v_1}{(\kOOconsI{e_2}{\rho}{\kappa})}}{
%	\sOOinspect{e_2}{\rho}{cont(\kOOconsII{v_1}{\kappa})}}{}
%
%\redrule{
%\sOOreturn{v_2}{(\kOOconsII{v_1}{\kappa})}}{
%\sOOreturn{(\hcvOOcons{v_1}{id(T_1)}{v_2}{id(T_2)})}{\kappa}}{
%\\&&
%\sidecond{v_1 : T_1 \wedge v_2 : T_2}}
%
%\redrule{
%\sOOreturn{v}{(\kOOinl{\kappa})}}{
%\sOOreturn{(\hcvOOinl{v}{id(T)})}{\kappa}}{
%\\&&
%\sidecond{v : T}}
%
%\redrule{
%\sOOreturn{v}{(\kOOinr{\kappa})}}{
%\sOOreturn{(\hcvOOinr{v}{id(T)})}{\kappa}}{
%\\&&
%\sidecond{v : T}}
%
%\redrule{
%\sOOreturn{v_1}{(\kOOappI{e_2}{\rho}{\kappa})}}{
%\sOOinspect{e_2}{\rho}{cont(\kOOappII{v_1}{\kappa})}}{}
%
%	
%	& \vdots \\
%	\redruleS{
%		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
%	}{
%		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
%	}{}
%	\redruleS{
%		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
%	}{
%		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
%	}{}
%	\redruleS{
%		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
%	}{
%		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
%	}{}
%	\redruleS{
%		
%\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
%	}{
%		\begin{cases}
%		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)} \\
%		\;\;\;\;\;\;\;\;\;\sidecond{applyCast(v,c_1) = \rOOsucc{v'}} 
%		\\
%		\sOOhalt{(\oOOblame{l})} \\
%		\;\;\;\;\;\;\;\;\;\sidecond{applyCast(v,c_1) = \rOOfail{l}}
%		\end{cases}
%		
%	}{}
	\end{array}
	\]

@@

\subsection{Relating Some \effCEK{C} to \ineffCEKD}
\label{secc:framework:monoid-correct}

In this subsection, we prove that if a instance of Cast ADT $C$ is Lazy D and 
is a monoid, then $eval_\mathcal{D} = eval_{\mathcal{S}(C)}$. We proof this 
theorem with a weak bisimulation between \effCEK{C} and \ineffCEKD.

Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation. Here we omit rules 
that make the relation a congruence.

\begin{figure}
	\fbox{$\text{\effCEK{C}} \approx \text{\ineffCEKD}$}
	\[\dots\]

	\fbox{$\kappa \approx \kappa$}
	\begin{gather*}
	\inference{
		k \approx \kappa
	}{
		cont(k) \approx \kappa
	}
	\quad
	\inference{
		\kappa_1 \approx \kappa_2
	}{
		ext(cast(T_1,l,T_2),\kappa_1) \approx 
		\kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa_2}
	}
	\end{gather*}

	\fbox{$v \approx v$}
	\begin{gather}
	\inference{
		v_1 \approx v_2 &
		v_2 : P
	}{
		\hcvOOinj{P}{v_1} \approx \vOOcast{v_2}{\cOOcast{P}{l}{\TOOdyn}}
	}
	\quad
	\inference{}{
		\hcvOOtt \approx \vOOtt
	}
	\quad
	\inference{}{
		\hcvOOtt \approx \vOOcast{\vOOtt}{\cOOcast{\POOunit}{l}{\POOunit}}
	}
	\\
	\inference{
		\rho_1 \approx \rho_2 &
		dom(\rho_1) = dom(\rho_2) = \Gamma \\
		\Gamma , x : T_1 \vdash e : T_2
	}{
		\hcvOOfun{id(T_1)}{\rho_1}{x}{e}{id(T_2)}
		\approx
		\vOOfun{\rho_2}{x}{e}
	}
	\quad
	\inference{
		v_1 \approx v_2 & v_3 \approx v_4 &
		\judgeType{v_1}{T_1} &
		\judgeType{v_3}{T_2}
	}{
		\hcvOOcons{v_1}{id(T_1)}{v_3}{id(T_2)}
		\approx
		\vOOcons{v_2}{v_3}
	}
	\\
	\inference{
		\hcvOOfun{c_1}{\rho}{x}{e}{c_2} \approx v_2 \\
%		\judgeType{\hcvOOfun{c_1}{\rho}{x}{e}{c_2}}{\POOfun{T_1}{T_2}} \\
		\judgeType{v_2}{\POOfun{T_1}{T_2}} \\
		c_1' = seq(cast(T_3,l,T1),c_1) \\
		c_2' = seq(c_2,cast(T_2,l,T_4))
	}{
		\hcvOOfun{c_1'}{\rho}{x}{e}{c_2'}
		\approx
		\vOOcast{v}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}}
	}
	\quad
	\inference{
		\hcvOOcons{v_1}{c_1}{v_3}{c_2} \approx v_2 \\
		\judgeType{v_2}{\POOprod{T_1}{T_2}} \\
		c_1' = seq(c_1,cast(T_1,l,T_3)) \\
		c_2' = seq(c_2,cast(T_2,l,T_4))
	}{
		\hcvOOcons{v_1}{c_1'}{v_3}{c_2'} \approx
		\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{\POOprod{T_3}{T_4}}}
	}
	\\
	\inference{
		v_1 \approx v_2 & v_1 : T
	}{
		\hcvOOinl{v_1}{id(T)} \approx \vOOinl{v_2}
	}
	\quad
	\inference{
		\hcvOOinl{v_1}{c} \approx v_2 &
		v_2 : \POOsum{T_1}{T_2} &
		c' = seq(c,cast(T_1,l,T_3))
	}{
		\hcvOOinl{v_1}{c'} \approx
		\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
	}
	\\
	\inference{
	v_1 \approx v_2 & v_1 : T
	}{
	\hcvOOinr{v_1}{id(T)} \approx \vOOinr{v_2}
	}
	\quad
	\inference{
	\hcvOOinr{v_1}{c} \approx v_2 &
	v_2 : \POOsum{T_1}{T_2} &
	c' = seq(c,cast(T_2,l,T_4))
	}{
	\hcvOOinr{v_1}{c'} \approx
	\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
	}
	\end{gather}
	\caption{Bisimulation between \effCEK{C} and \ineffCEKD}
	\label{fig:bisim-SC-D}
\end{figure}

@@

The relation between values is more special. When the \ineffCEKD\ value is 
non-casted, the casts in the \effCEK{C} value are identity. Otherwise, we push 
the cast into the value constructors, except injections. For examples: 
\begin{gather*}
\inference{
	v_1, v_2 : P &
	v_1 \approx v_2
}{
	\hcvOOinj{P_1}{v_1} \approx \vOOcast{v_2}{\cOOcast{P}{l}{\TOOdyn}}
}
\quad
\inference{
	v_1, v_2 : T &
	v_1 \approx v_2
}{
	\hcvOOinl{v_1}{id(T)} \approx \vOOinl{v_2}
}
\\
\inference{
	(\hcvOOinl{v}{c}, v_2) : \POOsum{T_1}{T_2}
}{
	\hcvOOinl{v}{seq(c,cast(T_1,l,T_3))} \approx 
	\vOOcast{v_2}{\cOOcast{T_1}{l}{T_3}}
}
%\quad
%\inference{
%	\Gamma , x : T_1 \vdash T_2 &
%	\rho_1 \approx \rho_2
%}{
%	\hcvOOfun{id(T_1)}{\rho_1}{x}{e}{id(T_2)} \approx \vOOfun{\rho_2}{x}{e}
%}
%\quad
%\inference{
%	\hcvOOcons{v_1}{c_1}{v_2}{c_2}
%	\approx
%	v
%}{
%	\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))}
%}
%\\
%\inference{
%	\hcvOOfun{c_1}{\rho}{x}{e}{c_2} : \POOfun{T_1}{T_2} &
%	\hcvOOfun{c_1}{\rho}{x}{e}{c_2} \approx v
%}{
%	\hcvOOfun{seq(cast(T_3,l,T_1), c_1)}{\rho}{x}{e}{seq(c_2,cast(T_2,l,T_4))}
%	\approx
%	\vOOcast{v}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T3}{T_4}}}
%}
\end{gather*}
